\framework: Morphology-based Entity and Relational Entity Extraction Framework for Arabic

### 2018-03-16 tex/merf/TALMajor/abstract.tex
In progress: merging motivation with section 3

Rule-based techniques and tools to extract {\em entities} and {\em relational entities} from documents allow users to specify desired entities using natural language questions, finite state automata, regular expressions, structured query language statements, or proprietary scripts.  These techniques and tools require expertise in linguistics and programming and lack support of Arabic {\em morphological analysis} which is key to process Arabic text.
In this work, we present \framework; a morphology-based entity and relational entity extraction framework for Arabic text.  \framework provides a friendly interface where the user, with basic knowledge of linguistic features and regular expressions, defines {\em tag types} and interactively associates them with regular expressions defined over Boolean formulae. Boolean formulae range over matches of Arabic morphological features, and synonymity features. Users define relations with tuples of subexpression matches and can associate code actions with subexpressions. \framework computes feature matches, regular expression matches, and constructs entities and relational entities from the user-defined relations. We evaluated our work with several case studies and compared with existing application-specific techniques. The results show that \framework requires shorter development time and effort compared to existing techniques and produces reasonably accurate results within a reasonable overhead in run time.

>>>>

Rule-based techniques and tools to extract entities and relational entities from documents allow users to specify desired entities using natural language questions, finite state automata, regular expressions, structured query language statements, or proprietary scripts.
These techniques and tools require expertise in linguistics and programming and they lack support of Arabic {\em morphological analysis} which is key to process Arabic text.
In this work, we present \framework; a morphology-based entity and relational entity extraction framework for Arabic text.
\framework provides a friendly interface where the user, with basic knowledge of linguistic features and regular expressions, defines {\em tag types} and interactively associates them with regular expressions defined over Boolean formulae.
Boolean formulae range over matches of Arabic morphological features, and synonymity features.
Users define relations with tuples of subexpression matches and can associate code actions with subexpressions.
\framework computes feature matches, regular expression matches, and constructs entities and relational entities from the user-defined relations.
We evaluated our work with several case studies and compared with existing application-specific techniques.
The results show that \framework requires shorter development time and effort compared to existing techniques and produces reasonably accurate results within a reasonable overhead in run time.

### 2018-03-16 tex/merf/TALMajor/introduction.tex
In progress: merging motivation with section 3

In this paper, 
we present \framework, a {\em morphology-based entity and relational entity
extraction framework for Arabic text }. 
\framework provides a user-friendly interface where the user defines tag types 
and associates them with \framework formulae that are regular expressions over 
\framework Boolean formulae. 
Boolean formulae are terms, negations of terms, and disjunctions of terms. 
Terms are matches to Arabic morphological features including 
prefix, stem, suffix, part of speech (POS) tags, gloss tags, extended synonym tags, 
and semantic categories. 
We discuss the importance of the morphological features supported in 
\framework terms in Section~\ref{sec:morph}; in brief, morphological preprocessing
is key to Arabic NLP.% due to the richness of Arabic morphology.

We illustrate the target of \framework using a simple example. 
Consider the text in Figure~\ref{fig:intromotiv} which contains
directions to Dubai Mall~\footnote{text taken from the Dubai Mall website
~\url{http://www.thedubaimall.com/ar/}}.
The framed words in the text are entities referring to names of people 
($n_1,n_2,n_3$), 
names of places ($p_1,\dots,p_7$), 
relative positions ($r_1,\dots,r_4$), 
and numerical terms ($u_1,u_2$). 
We would like to extract those entities, and then extract
the relational entities forming the graph in Figure~\ref{fig:intromotiv} 
where vertices express entities, 
and edges represent the relational entities.
\framework allows a regular user to do that interactively
in four phases that include morphological analysis, 
entity extraction based on morphological features, 
relational entity extraction, and entity cross-reference.

@@

\framework takes an Arabic text, a set of user-defined \framework Boolean 
formulae, and a set of user-defined \framework regular expressions. 
\framework computes the morphological solutions of the words in the 
input text then computes matches to the Boolean formulae. 
\framework then generates a {\em non-deterministic finite state 
automata} (NDFSA) for each expression and simulates it with the 
sequence of Boolean formulae matches to compute the regular 
expression matches. 
\framework generates executable code for the actions associated with
the regular expressions, 
compiles, links, and executes the generated code 
as shared object libraries. 
Finally, \framework constructs the semantic relations and 
cross-reference between entities. 
\framework also provides visualization tools to present the matches, 
and estimate their accuracy with respect to reference tags.

\subsection{Existing annotation and entity extraction tools}

Researchers proposed and evaluated empirical and 
knowledge-based techniques to extract entities and relational entities
from text. 
We briefly review them here and we discuss them and compare to them
in Section~\ref{sec:related}. 
The work in~\cite{ekbal2010named} presents a language independent 
approach for NER extraction using {\em support vector machines}. 
The work in~\cite{abdelrahman2010integrated} integrates 
a semi-supervised bootstrapping pattern recognition technique, 
and a supervised classifier based on {\em conditional random fields}
to solve NER problems.

Knowledge-based techniques such 
as~\cite{zaghouani2010adapting,traboulsi2009arabic} propose local grammars 
with morphological stemming to perform NER. 
%The work in~
\cite{ZaMaHaCicling2012Entity} presents a method for extracting entities, 
events, and relations amongst them from Arabic text using a hierarchy of manually built 
finite state machines driven by morphological features and graph 
transformation algorithms. 
Such techniques require advanced linguistic and programming expertise. 
QARAB is a question answering system that takes 
Arabic natural language queries and provides short answers~\cite{hammo2002qarab}.

Researchers also proposed systems for automatic IE based 
on user specifications. 
CPSL is a common pattern specification language for finite-state 
grammar~\cite{appelt1998common}. 
%\framework is an extension to CPSL with action execution and relation construction. 
%It defines three sections for declaration, rule definition, and macros. 
The work in \cite{chiticariu2010systemt} presents SystemT, a system based on 
an algebraic Approach to Declarative information extraction (IE). 
%It uses a declarative rule language and an optimizer. 
TEXTMARKER is a rule-based IE system designed to extract structured data from 
text \cite{atzmueller2008rule}. 
\cite{urbain2012user} presents a user-driven relational model 
requiring a user natural language query to extract entities and relational entities.

This work significantly extends the position 
paper~\cite{JaZaMatar} that allows for manual, and 
basic morphology annotation.
\framework enables a regular user to incrementally create 
complex annotations for Arabic text based on automatic 
extraction of morphological tags through a user friendly interactive interface. 
\framework has the following advantages.
\begin{itemize}
  \item \framework provides a novel and intuitive visual interface to build Boolean formulae over morphological features, 
    build regular expressions over the resulting Boolean formulae, and thereafter compute automatic tags.
  \item To our knowledge, this morphology-based framework  is the first for Arabic entity and relational entity extraction.
  \item \framework provides the user with the ability to rapidly create annotated Arabic text corpora with sophisticated morphology-based tags.
\end{itemize}

@@

\input{directionMBFMRE}

In the rest of this paper,
Section~\ref{sec:motivation} presents a motivational example. 
Section~\ref{sec:morph} introduces Arabic morphological analysis 
and its important role in Arabic NLP. 
%We present preliminaries necessary to understand the work 
%in Section~\ref{sec:preliminaries}. 
Section~\ref{sec:framework} explains the \framework methodology. 
Section~\ref{sec:gui} presents the visual and user friendly interface of \framework. 
Section~\ref{sec:related} presents and discusses related work.
Section~\ref{sec:results} presents the evaluation results. 
Finally, we conclude and discuss future work in Section~\ref{sec:conclusion}.

>>>>

In this paper, 
we present \framework, a morphology-based entity and relational entity
extraction framework for Arabic text.
\framework provides a user-friendly interface where the user defines tag types 
and associates them with
%\framework formulae that are 
regular expressions over 
%\framework
Boolean formulae.
A Boolean formula is defined by a term, negation of a term, or disjunction of terms.
Terms are matches to Arabic morphological features including 
prefix, stem, suffix, part of speech (POS) tags, gloss tags, extended synonym tags, and semantic categories.
We often refer to regular expressions and Boolean formulae as expressions and formulae, respectively, for short.
%We discuss the importance of the morphological features supported in 
%\framework terms in Section~\ref{sec:morph}; in brief, morphological preprocessing
%is key to Arabic NLP.% due to the richness of Arabic morphology.

We illustrate the target of \framework using a simple example.
Consider the text in Figure~\ref{fig:intromotiv} which contains
directions to Dubai Mall~\footnote{text taken from the Dubai Mall website
~\url{http://www.thedubaimall.com/ar/}}.
The figure also presents a transliteration and an English translation of the Arabic text.
The framed words in the text are entities referring to names of people 
($n_1,n_2,n_3$), 
names of places ($p_1,\dots,p_7$), 
relative positions ($r_1,\dots,r_4$), 
and numerical terms ($u_1,u_2$). 
We would like to extract those entities, and then extract
the relational entities forming the graph in Figure~\ref{fig:intromotiv} 
where vertices express entities, 
and edges represent the relational entities.
\framework allows a regular user to do that interactively
in four phases that include morphological analysis, 
entity extraction based on morphological features, 
relational entity extraction, and entity cross-reference.

@@

\framework takes an Arabic text, a set of user-defined Boolean 
formulae, and a set of user-defined regular expressions.
\framework computes the morphological solutions of the words in the 
input text then computes matches to the Boolean formulae.
\framework then generates a {\em non-deterministic finite state 
automata} (NDFSA) for each expression and simulates it with the 
sequence of Boolean formulae matches to compute the regular 
expression matches. 
\framework generates executable code for the actions associated with
the regular expressions, 
compiles, links, and executes the generated code 
as shared object libraries.
Finally, \framework constructs the semantic relations and 
cross-reference between entities.
\framework also provides visualization tools to present the matches, 
and estimate their accuracy with respect to reference tags.

This work significantly extends the position paper~\cite{JaZaMatar} that allows for manual, and basic morphology annotation.
\framework enables a regular user to incrementally create 
complex annotations for Arabic text based on automatic 
extraction of morphological tags through a user friendly interactive interface. 
\framework has the following advantages.
\begin{itemize}
  \item \framework provides a novel and intuitive visual interface to build formulae over morphological features, 
    build regular expressions over the resulting formulae, and thereafter compute automatic tags.
  \item To our knowledge, this morphology-based framework is the first for Arabic entity and relational entity extraction.
  \item \framework provides the user with the ability to rapidly create annotated Arabic text corpora with sophisticated morphology-based tags.
\end{itemize}

@@

The rest of the paper is structured as follows.
%In the rest of this paper,
%Section~\ref{sec:motivation} presents a motivational example. 
Section~\ref{sec:morph} introduces Arabic morphological analysis 
and its important role in Arabic NLP.
%We present preliminaries necessary to understand the work 
%in Section~\ref{sec:preliminaries}. 
Section~\ref{sec:framework} explains the \framework methodology. 
Section~\ref{sec:gui} presents the visual and user friendly interface of \framework. 
Section~\ref{sec:related} presents and discusses related work.
Section~\ref{sec:results} presents the evaluation results. 
Finally, we conclude and discuss future work in Section~\ref{sec:conclusion}.

### 2018-03-16 tex/merf/TALMajor/relatedwork.tex
In progress: merging motivation with section 3

>>>>

\begin{comment}
\subsection{Existing annotation and entity extraction tools}

Researchers proposed and evaluated empirical and 
knowledge-based techniques to extract entities and relational entities
from text. 
We briefly review them here and we discuss them and compare to them
in Section~\ref{sec:related}. 
The work in~\cite{ekbal2010named} presents a language independent 
approach for NER extraction using {\em support vector machines}. 
The work in~\cite{abdelrahman2010integrated} integrates 
a semi-supervised bootstrapping pattern recognition technique, 
and a supervised classifier based on {\em conditional random fields}
to solve NER problems.

Knowledge-based techniques such 
as~\cite{zaghouani2010adapting,traboulsi2009arabic} propose local grammars 
with morphological stemming to perform NER. 
%The work in~
\cite{ZaMaHaCicling2012Entity} presents a method for extracting entities, 
events, and relations amongst them from Arabic text using a hierarchy of manually built 
finite state machines driven by morphological features and graph 
transformation algorithms. 
Such techniques require advanced linguistic and programming expertise. 
QARAB is a question answering system that takes 
Arabic natural language queries and provides short answers~\cite{hammo2002qarab}.

Researchers also proposed systems for automatic IE based 
on user specifications. 
CPSL is a common pattern specification language for finite-state 
grammar~\cite{appelt1998common}. 
%\framework is an extension to CPSL with action execution and relation construction. 
%It defines three sections for declaration, rule definition, and macros. 
The work in \cite{chiticariu2010systemt} presents SystemT, a system based on 
an algebraic Approach to Declarative information extraction (IE). 
%It uses a declarative rule language and an optimizer. 
TEXTMARKER is a rule-based IE system designed to extract structured data from 
text \cite{atzmueller2008rule}. 
\cite{urbain2012user} presents a user-driven relational model 
requiring a user natural language query to extract entities and relational entities.
\end{comment}

### 2018-03-16 tex/merf/TALMajor/sarf.tex
In progress: merging motivation with section 3

We denote by 
\ss,
\pp,
\xx,
\PP,
\GG, and 
\AC, the set of 
all stems,
prefixes,
suffixes,
POS,
gloss, 
and user defined category tags, respectively. 
Let $T=\langle t_1,t_2,\ldots,t_M\rangle$ be a set of Arabic words denoting the 
text documents. 
\framework uses Sarf to compute a set of morphological solutions $M(t)=\{m_1,m_2,\ldots,m_N\}$
for each word $t\in T$. 
Each morphological solution $m\in M(t)$ is a tuple of the form 
$\langle p,s,x,P,G,C\rangle\in \pp \times  \ss\times \xx\times \PP\times\GG \times \AC$.

@@

\input{MERFOverview}

>>>>

We denote by 
\ss,
\pp,
\xx,
\PP,
\GG, and 
\AC, the set of 
all stems,
prefixes,
suffixes,
POS,
gloss, 
and user defined category tags, respectively. 
Let $T=\langle t_1,t_2,\ldots,t_M\rangle$ be a set of Arabic words denoting the 
text documents. 
\framework uses Sarf to compute a set of morphological solutions $M(t)=\{m_1,m_2,\ldots,m_N\}$
for each word $t\in T$. 
Each morphological solution $m\in M(t)$ is a tuple of the form 
$\langle p^k,s,x^l,P,G,C\rangle\in \pp^k \times  \ss\times \xx^l\times \PP\times\GG \times \AC$ where $k>0$ and $l>0$ indicate possibly multiple prefixes and suffixes, respectively.

@@

### 2018-03-16 tex/merf/TALMajor/tool.tex
In progress: merging motivation with section 3

@@

The sets $E, A,$ and $L$ denote all English words, Arabic words, 
and Arabic lexicon words, respectively. 
We have $\GG \subset E$ and $\ss \subset L \subset A$. 
Function $\alpha: \ss \rightarrow 2^{\GG}$ maps Arabic stems to 
subsets of related English glosses. %; e.g. $g_{s} = \alpha(s)\subset 2^{\GG}$.
Function $\gamma: L \rightarrow 2^{\ss}$ maps Arabic lexicon words to subsets 
of relevant Arabic stems. %; e.g. $s_{l} = \gamma(l)\subset 2^{\ss}$.

@@

The example in Figure~\ref{fig:introsynEx} illustrates the computation. 
The word \RL{mA'}is related to \RL{n.d.h}through the gloss intersection \cci{water}. 
The $Syn^2$ feature relates 
the words \RL{mA'} and ``\RL{r^s^s}'' since \RL{n.d.h} and \RL{r^s^s} 
have the gloss intersection \cci{spray}.

@@

Let ${\cal O} = \{ \mathit{isA}, \mathit{contains}\}$ be the set of atomic term 
predicates, and let ${\cal F} = \{ \pp, \ss, \xx, \PP, \GG, \AC\}$ be the 
set of morphological features. 
Given a word $w$, a morphological feature $A\in{\cal F}$, 
a user defined constant feature value $CF\in A$, and an integer 
$k, 1\le k\le 7$, 
the following are morphology-based atomic terms (MAT). 
\begin{itemize}
  \item $a(w):= \exists m \in M(w). m=\langle p,s,x,P,G,C\rangle. r \circ CF$
where $\circ \in {\cal O}$, $r \in \{p,s,x,P,G,C\}$, and $r\in A$.
Informally, a solution vector of $w$ exists with
a feature containing (or exactly matching) $CF$. 
\item $a(w) := w \in Syn^k(CF), CF \in \ss$.
  Informally, this checks $w$ is an extended synonym of a stem $CF$. 
\end{itemize}

A morphology-based Boolean formula (MBF) is of the following form. 
\begin{itemize}
  \item $a$ and $\neg a$ are MBF formulae where $a$ is a MAT and $\neg$ is the negation operator. 
  \item $(f \vee g)$ is an MBF where $f$ and $g$ are MBF formulae, 
    and $\vee$ is the disjunction (union) operator. 
\end{itemize}
Formula $N$ in Figure~\ref{fig:motiv} checks whether a solution has a category
feature matching category {\tt Name\_of\_Person}.
Formula $R$ is the disjunction of MAT terms that check for
solutions matching stems such as \RL{qrb} (near) and \RL{fy} (in).

A morphology-based regular expression (MRE) is one of the following. 
\begin{itemize}
\item $m$ is an MRE where $m$ is an MBF.
\item $fg$ is an MRE denoting a concatenation operation
  where $f$ and $g$ are both MRE expressions. This is 
  satisfied by a match of $f$ followed by a match of $g$. 
\item $f*,f+,f$\textasciicircum$x,$ and $f?$ are MRE expressions where $f$ is an MRE,
  and are satisfied by zero or more matches, one of more matches, up to $x$ matches, 
  and zero or only one match of $f$, respectively.
\item $f\& g,$ (conjunction) and $f|g$ (disjunction) are  MRE expressions where 
  $f$ and $g$ are MRE expressions, and are satisfied by a 
  a match of both $f$ and $g$, 
  and a match of either $f$ or $g$, respectively. 
\end{itemize}
We denote by $\ldbrack f\rdbrack$ the set of matches of an MRE $f$.

>>>>

\input{MERFOverview}

@@

The motivation for $Syn^k$ is to construct a light Arabic ontology based on the lexicon of Sarf.
The sets $E, A,$ and $L$ denote all English words, Arabic words, 
and Arabic lexicon words, respectively.
Recall that $\GG$ and $\ss$ denote the set of glosses and stems in the morphological analyzer, respectively.
We have $\GG \subset E$ and $\ss \subset L \subset A$. 
Function $\alpha: \ss \rightarrow 2^{\GG}$ maps Arabic stems to 
subsets of related English glosses. %; e.g. $g_{s} = \alpha(s)\subset 2^{\GG}$.
Function $\gamma: L \rightarrow 2^{\ss}$ maps Arabic lexicon words to subsets 
of relevant Arabic stems. %; e.g. $s_{l} = \gamma(l)\subset 2^{\ss}$.

@@

The example in Figure~\ref{fig:introsynEx} illustrates the computation.
The input Arabic word \RL{mA'}, denoted $w$, shares the gloss \cci{water} with the stem \RL{n.d.h}, denoted $s_1$, i.e. $s_1\in Sy^{1}(w)$.
%The input word \RL{mA'} shares the gloss \RL{n.d.h} through the gloss intersection \cci{water}. 
Next, the stem \RL{r^s^s}, denoted $s_2$, shares the gloss \cci{spray} with $s_1$, i.e. $s_2\in Sy^{1}(s1)\subset Sy^{2}(w)$.
Therefore, $Syn^2(w)$ relates the words \RL{mA'} and \RL{r^s^s}.

@@

Let ${\cal O} = \{ \mathit{isA}, \mathit{contains}\}$ be the set of atomic term 
predicates, and let ${\cal F} = \{ \pp, \ss, \xx, \PP, \GG, \AC\}$ be the 
set of morphological features where each entry is in turn a set of values for that feature.
Given a word $w$, a morphological feature $A\in{\cal F}$, 
a user defined constant feature value $CF\in A$, and an integer 
$k, 1\le k\le 7$, 
the following are morphology-based atomic terms (MAT), {\em terms} for short.
\begin{itemize}
  \item $a(w):= \exists m \in M(w). m=\langle p^k,s,x^l,P,G,C\rangle. r \circ CF$
where $\circ \in {\cal O}$, $r \in \{p^k,s,x^l,P,G,C\}$, and $r\in A$.
Informally, a solution vector of $w$ exists with
a feature containing or exactly matching $CF$.
The predicates $\mathit{isA}$ and $\mathit{contains}$ denote the exact match and contain criteria, respectively.
\item $a(w) := w \in Syn^k(CF), CF \in \ss$.
  Informally, this checks if $w$ is an extended synonym of a stem $CF$. 
\end{itemize}

A morphology-based Boolean formula (MBF) is of the following form.
\begin{itemize}
  \item $a$ and $\neg a$ are MBF formulae where $a$ is a MAT and $\neg$ is the negation operator. 
  \item $(f \vee g)$ is an MBF where $f$ and $g$ are MBF formulae, 
    and $\vee$ is the disjunction (union) operator. 
\end{itemize}

Moreover, \framework provides $O$ to be a default Boolean formula that tags all {\em other} words in the text that do not match a user defined formula.
We also refer to those words as {\em null} words.

\input{directionMBF}

Consider the task we discussed in the introduction (Figure~\ref{fig:intromotiv}) 
and recall that we are interested in identifying names of people, names of places, relative positions, and numerical terms.
The table in Figure~\ref{fig:taskMBF} presents the defined formulae.
The user denotes the ``name of person'' entities with formula $N$ 
which requires the {\em category} feature in the morphological solution of a word to be {\tt Name\_of \_Person}.
The entities $n_1$, $n_2$, and $n_3$ are matches of the formula $N$ in the text.
Similarly, the user specifies formula $P$ to denote ``name of place'' entities. 
The user specifies formula $R$ to denote ``relative position'' entities, 
and defines it as a disjunction of MAT terms that check for 
solutions matching stems such as \RL{qrb} (near) and \RL{fy} (in).
%requires the stem feature of a word to belong to a selected list of stems containing \RL{fy} and \RL{qrb}. a
Similarly, $U$ denotes numerical terms and is a disjunction of constraints 
requiring the stem feature to belong to a set of stems such as
\RL{'wl}(first), \RL{_tAny}(second), \dots \RL{`A^sr}(tenth).

%Formula $N$ in Figure~\ref{fig:motiv} checks whether a solution has a category feature matching category {\tt Name\_of\_Person}.
%Formula $R$ is the disjunction of MAT terms that check for solutions matching stems such as \RL{qrb} (near) and \RL{fy} (in).

Next, we define a morphology-based regular expression (MRE) as follows.
\begin{itemize}
\item $m$ is an MRE where $m$ is an MBF.
\item $fg$ is an MRE denoting a concatenation operation
  where $f$ and $g$ are both MRE expressions. This is 
  satisfied by a match of $f$ followed by a match of $g$. 
\item $f*,f+,f$\textasciicircum$x,$ and $f?$ are MRE expressions where $f$ is an MRE,
  and are satisfied by zero or more matches, one of more matches, up to $x$ matches, 
  and zero or only one match of $f$, respectively.
\item $f\& g,$ (conjunction) and $f|g$ (disjunction) are  MRE expressions where 
  $f$ and $g$ are MRE expressions, and are satisfied by a 
  a match of both $f$ and $g$, 
  and a match of either $f$ or $g$, respectively. 
\end{itemize}
We denote by $\ldbrack f\rdbrack$ the set of matches of an MRE $f$.

Back to the example in Figure~\ref{fig:intromotiv}.
We use the formulae defined in Figure~\ref{fig:directionMBF} to construct an MRE such as
$(P|N)\!+~O?~R~O^\wedge\!2~(P|N|U)+$ where 
$|,+,?,$ and $^\wedge k$ denote disjunction, one or more, zero or one, and
up to $k$ matches, respectively.
The expression specifies a sequence of places or names of persons, 
optionally followed by a null word, 
followed by one relative position, followed by up to two possible null words, 
followed by one or more match of name of place, name of person, or numerical term.
$O?$ and $O^\wedge 2$ are used in the expression to allow for flexible matches.
%The user reaches the satisfying matches by experimenting with the visualizer and the expression editor which do not require knowledge and expertise in regular expressions.

\input{directionMRE}

The match trees in Figure~\ref{fig:taskMRE} illustrate two matches of the expression computed by \framework.
The first match tree refers to the text 
\RL{brj _hlyfT bAlqrb mn AltqA.t` Al-'wl}(Khalifa Tower next to the first intersection).
The second match tree refers to the text 
\RL{dby mwl `l_A mqrbT mn h_dA Almbn_A}(Dubai Mall is located near this building).
The leaf nodes of the trees are entities and the edges and internal nodes are text, 
morphology-based, 
and word distance based relational entities.
